The Concurrent Calculi Formalisation Benchmark

### 2023-10-11 paper/paper.tex
rework scope extrusion

For our challenge on linear reasoning we have chosen a safety theorem for a session type system since this allows us to involve linear reasoning without many definitions.
For the same reason we have chosen not to include delegation of channels in the syntax and to use a reduction semantics instead of a transition system semantics.

@@

Inspired by Vasconcelos~\cite{Vasconcelos2012}, we use a syntax where restriction binds two variables.
We have chosen this presentation to make the duality of names obvious in the type system.

The notion of well-formedness we have chosen for our challenge problem is quite basic, and does not for instance consider deadlocked processes.
While more sophisticated notions of well-formedness are also interesting, the proofs of these properties are more complicated and would thus make the challenge problem more difficult and less focused on the linear aspects of the system.

>>>>

For our challenge on linear reasoning we have chosen a safety theorem
for a session type system since this allows us to involve linear
reasoning without many definitions. Accordingly, we have chosen not to
include channel delegation and to use a reduction instead of a
transition system semantics.

@@

Inspired by Vasconcelos~\cite{Vasconcelos2012}, we use a syntax where
restriction binds two variables. This presentation makes the duality
of the two names obvious in the type system.

We have simple notion of well-formedness for our challenge problem,
and does not for instance consider deadlocked processes. While more
sophisticated notions of well-formedness are also interesting, the
proofs of these properties are more complicated and would thus make
the challenge problem more difficult and less focused on the linear
aspects of the system.
